Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-02-18 tex/VHzQ.tex
further tex/VHzQ updates

We present all our photometry and magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}.  This includes the near-infrared, as well as the mid-infrared magnitudes. Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide range of optical, NIR and MIR filters. We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al. 2016) in order to be consistent with \citet{Banados2016} and all logarithms are to the base 10.

@@

\begin{table}
\begin{tabular}{l r r l}
\hline  \hline
Survey              & \# VH$z$Qs & (\%) & Notes/Survey reference  \\
\hline  
  ATLAS             &     4    &   ( 0.86)    &  \citet{Shanks2015} \\
  CFHQS            &   20    &   ( 4.32)    &  \citet{Willott2007} \\
  DELS               &   16    &   ( 3.46)    &  \citet{Dey2018} \\
  ELAIS              &     1    &   ( 0.22)    &  \citet{Vaisanen2000} \\
  FIRST              &     1    &   ( 0.22)    &  \citet{Becker1995} \\
  HSC                 &    8    &   ( 1.73)    & \citet{Miyazaki2018} \\
  IMS                 &     5    &   ( 1.08)     &  \citet{Kim2015} \\
  MMT               &   12    &   ( 2.59)     &  \citet{McGreer2013} \\
  NDWFS           &     1    &   ( 0.22)    &  \citet{JD1999} \\
  PSO                 &   83   &   (17.93)   &   \citet{Kaiser2002, Kaiser2010} \\
  RD                   &     1   &   ( 0.22)    &  \citet{Mahabal2005} \\
  SDSS                &  170  &    (36.72)    & \citet{EDR} \\
 SDWISE$^{b}$    &   27    &  ( 5.83)    &   \citet{WangF2016} \\
%% SHELLQs    &  $^{c}$63  &  (13.6)   &  \citet{Matsuoka2016} \\  %% if you include 8 objects from the first HSC paper...
  SHELLQs         &    55    &   (11.88)  &  \citet{Matsuoka2016}     \\  
  SUV$^{c}$       &   20     &    ( 4.32)  & \citet{YangJ2017} \\
  UHS               &    1      &  ( 0.22)     &  \citet{WangF2017} \\
  ULAS               &   10   &   ( 2.16)     & \citet{Lawrence2007} \\
  VDES$^{d}$       &   17  &    ( 3.67)     &  \citet{Reed2017} \\
  VHS                 &     1  &     ( 0.22)    & \citet{WangF2018b} \\
  VIK                 &     9    &  ( 1.94)    &  \citet{Edge2013} \\
  VIMOS           &    1      &  ( 0.22)     &   \citet{LeFevre2003} \\
\hline  \hline
\end{tabular}
\caption{The source and number of the VH$z$Q, with the key survey reference also given. 
  Recent survey name and acronyms include: 
  $^{a}$DESI Legacy Imaging Survey; 
  $^{b}$SDWISE = SDSS+WISE; 
  $^{a}$SUV  = SDSS-ULAS/VHS; 
  $^{c}$VDES = VHS/VIKING+DES; 
%  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.
}
      \label{tab:surveys}
\end{table}

@@

The redshifts for the VH$z$Qs generally come from the measurement of
broad UV/optical emission lines. Where there are far infra-red
emission lines e.g. \cii~158 micron, we report these, but at the level
of our current analysis broadline redshifts are sufficient.

@@

\subsection{Optical Photometry}
%\subsubsection{Pan-STARRS1 (PS1)} 
We query the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}} Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs) service at \href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}. The Pan-STARRS1 (PS1) survey observed the 30,000 deg$^{2}$ of sky north of declination $\delta = -30$ degrees in the five $grizy$ filters.  PS1 is the first part of Pan-STARRS to be completed and is the basis for the DR1. \citet{Chambers2016}, \citet{Magnier2016a}, \citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and \citet{Flewelling2016} describe the instrument, survey, and data analyses.  The principal science product of the PS1 survey is the catalog accessible through the CasJobs interface.

We query and return the mean PSF magnitudes from the $grizy$ filters ({\tt MeanPSFMag}) which are in the AB system for our 463 VH$z$Q sample. Details of our SQL and links to the main tables are given in Appendix~\ref{sec:PS1_SQL}.

    \iffalse
    \subsubsection{DECam} 
    The Dark Energy Camera \citep[DECam][]{Flaugher2015} is 
    is a wide-field imager with a 2.2 degree diameter field of view 
    mounted at the prime focus of the Victor M. Blanco 4 m telescope 
    at the Cerro Tololo International Observatory. We use data 
    from both the Dark Energy Survey \citep[DES; ][]{DES2016} and 
    the DESI Legacy Imaging Survey \citep[DECaLS; ][]{Dey2018}. 
    \fi

\subsection{Near-infrared photometry}~\label{sec:NIR_data} 
The near-infrared data in this paper comes from the Wide Field Astronomy Unit's
(WFAU) Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
\citep[WSA][]{WSA} and VISTA-VIRCAM, the VISTA Science Archive
\citep[VSA][]{VSA}. These archives were developed for the VISTA Data Flow System
\citep[VDFS][]{VDFS}.

We access both the WSA and the VSA and include all non-proprietary WFCAM data, which covers all
public surveys and PI projects from Semester 05A to 1st January 2017, and all
non-proprietary VISTA data, which covers all public surveys and PI projects from
science verification (20091015) to 1st April 2016.

The data was processed using a matched-aperture photometry method
where flux is measured at the spectroscopic position of the quasar,
without necessarily knowing if there is a formal detection in the NIR
photometry beforehand.  Full details of the matched-aperture pipeline
will appear in a forthcoming paper, Cross et al.  2018, in prep, and
has also been discussed in \citet{Cross2013}.

We query the WSA and VSA performing matched-aperature photometry at
the positions of our 463 VH$z$Qs. This database is world-readable and we give the full receipe
and relevant SQL queries for accessing both databases in Appendix~\ref{sec:SQL}.

    \subsubsection{Averaging matched photometry}
    The photometry in a single epoch image often has low
    signal-to-noise.  The advantage of matched aperture photometry on QSOs
    is that co-adding is relatively simple if each epoch is taken in the
    same aperture and the aperture photometry has been corrected to
    total. Indeed, the standard aperture corrections work well for point
    sources. Coadding using the matched-aperature photometry, where the
    individual epochs are taken from multiple projects with different
    pointings and orientations, should help with issues such as scattered
    light, pixel distortion and aperture corrections.

@@

    We calculate a set of averaged catalogues, for each pointing and filter, based
    on the requirements in \verb+RequiredMapAverages+, in these cases over time
    spans of 7, 14, 30, 91, 183 days, 365 days, 730 days, over 10 epochs and
    over all epochs. {\bf NJC: Should we add this table to suplemental online
    only material?} The averaging process starts at the first epoch and works on.

@@

    \subsubsection{Salient details of WSA and VSA}. 
    %% N.B.!!!    WFAU archives more than just the NIR Surveys -- it archives *all* the WFCAM and VISTA programmes!!
    In this study, we are not just quering the WSA or VSA data tables. 
    We are taking a list of objects (positions) are performing matched aperature (``forced'') photometry on the NIR imaging data. 
    As such, we generate a set of tables that are different in subtle ways to the regular ``Detection'' tables.

    The two most important tables for our needs are the {\tt [w/v]serv1000MapRemeasurement} and {\tt [w/v]serv1000MapRemeasAver}.

    Full documentation can be found at the \href{http://wsa.roe.ac.uk/www/wsa_browser.html}{WSA Schema Browser} 
and the \href{http://horus.roe.ac.uk/vsa/www/vsa_browser.html}{VSA Schema Browser}.

\subsection{MIR data}
Since we are concerned here with the very large area ($\gg1000$ deg$^2$) surveys, we leave exploration of the VH$z$Q population in e.g. the large Spitzer areal surveys such as the Spitzer IRAC Equatorial Survey \citep[SpIES; ][]{Timlin2016}, the Spitzer-HETDEX Exploratory Large-area Survey \citep[SHELA; ][]{Papovich2016} and the Spitzer-SPT Deep Field \citep[SSDF; ][]{Ashby2013}, to future investigation. This will also include a detailed study of MIR spectra e.g. \citet{Lambrides2018}.

The MIR data for this study comes from the Wide-field Infrared Survey Explorer (WISE) mission, and we utlize data from the WISE cryogenic and NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey phases.

We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fourth-year of NEOWISE-R operations \citep[2017 December;]{Mainzer2011}.  More specifically, we utilise the recently released ``unWISE Catalog'' \citet{MeisnerSchlafly2019}. The unWISE effort\footnote{http://unwise.me/} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}. {\bf Few more words here on the unWISE catalog}.

@@

Figure~\ref{fig:Opt_colourredshift} presents the optical
colour-redshift trends for Late Type M/L/T dwarfs and the VH$z$Qs.
\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_Optcolors_20180704.pdf}
   \centering
   \caption[]
   {Optical colour vs. spectral type and redshift for Late Type M/L/T dwarfs and the VH$z$Qs.
     The stars are M, L, and T dwarfs from the \citet{Best2018} PS1-detected catalog.  
   {\it N.B. Trying to look as good as Fig.~5 from Best et al. (2018). How does one get 
bigger gaps between subplots??}}
   \label{fig:Opt_colourredshift}
 \end{figure*}

@@

\iffalse
\subsection{SEDs and Dust properties of the VH$z$Qs}
There are a range of IR SEDs e.g. \citet{Mullaney2013} etc. etc. etc. 
However, they are, for our purposes all roughly the same.

\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/RestWavelength_flux_20180702.pdf}
  \centering
  \caption[]
  {The rest-frame properties of the VH$z$Qs. }
  \label{fig:RestWavelength_SEDs}
\end{figure*}
\fi

>>>>

We present all our photometry and magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}.  This includes the near-infrared, as well as the mid-infrared magnitudes. Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide range of optical, NIR and MIR filters. We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al. 2016) to be consistent with \citet{Banados2016} and all logarithms are to the base 10.

@@

\begin{table}
\begin{tabular}{l r r l}
\hline  \hline
Survey              & \# VH$z$Qs & (\%) & Survey reference  \\
\hline  
  ATLAS             &     4    &   ( 0.86)    &  \citet{Shanks2015} \\
  CFHQS            &   20    &   ( 4.32)    &  \citet{Willott2007} \\
  DELS               &   16    &   ( 3.46)    &  \citet{Dey2018} \\
  ELAIS              &     1    &   ( 0.22)    &  \citet{Vaisanen2000} \\
  FIRST              &     1    &   ( 0.22)    &  \citet{Becker1995} \\
  HSC                 &    8    &   ( 1.73)    & \citet{Miyazaki2018} \\
  IMS                 &     5    &   ( 1.08)     &  \citet{Kim2015} \\
  MMT               &   12    &   ( 2.59)     &  \citet{McGreer2013} \\
  NDWFS           &     1    &   ( 0.22)    &  \citet{JD1999} \\
  PSO                 &   83   &   (17.93)   &   \citet{Kaiser2002, Kaiser2010} \\
  RD                   &     1   &   ( 0.22)    &  \citet{Mahabal2005} \\
  SDSS                &  170  &    (36.72)    & \citet{EDR} \\
 SDWISE$^{b}$    &   27    &  ( 5.83)    &   \citet{WangF2016} \\
%% SHELLQs    &  $^{c}$63  &  (13.6)   &  \citet{Matsuoka2016} \\  %% if you include 8 objects from the first HSC paper...
  SHELLQs         &    55    &   (11.88)  &  \citet{Matsuoka2016}     \\  
  SUV$^{c}$       &   20     &    ( 4.32)  & \citet{YangJ2017} \\
  UHS               &    1      &  ( 0.22)     &  \citet{WangF2017} \\
  ULAS               &   10   &   ( 2.16)     & \citet{Lawrence2007} \\
  VDES$^{d}$       &   17  &    ( 3.67)     &  \citet{Reed2017} \\
  VHS                 &     1  &     ( 0.22)    & \citet{WangF2018b} \\
  VIK                 &     9    &  ( 1.94)    &  \citet{Edge2013} \\
  VIMOS           &    1      &  ( 0.22)     &   \citet{LeFevre2003} \\
\hline  \hline
\end{tabular}
\caption{The source and number of the VH$z$Q, with the key survey reference also given. 
  Recent survey name and acronyms include: 
  $^{a}$DESI Legacy Imaging Survey; 
  $^{b}$SDWISE = SDSS+WISE; 
  $^{a}$SUV  = SDSS-ULAS/VHS; 
  $^{c}$VDES = VHS/VIKING+DES; 
%  $^{c}$Includes 8 objects with a HyperSuprimeCam \citep[HSC; ][]{Miyazaki2018} designation.
}
      \label{tab:surveys}
\end{table}

@@

The redshifts for the VH$z$Qs generally come from the measurement of
broad UV/optical emission lines. There are far infra-red emission
lines e.g. \cii~158 micron available for several objects, but at the
level of our current analysis broadline redshifts are sufficient.

@@

\subsection{Optical Photometry}
We query the Panoramic Survey Telescope and Rapid Response System
(Pan-STARRS)\footnote{\href{https://outerspace.stsci.edu/display/PANSTARRS}{https://outerspace.stsci.edu/display/PANSTARRS}}
Data Release 1 (DR1) Catalog Archive Server Jobs System (CasJobs)
service at
\href{http://mastweb.stsci.edu/ps1casjobs/}{mastweb.stsci.edu/ps1casjobs/}. The
Pan-STARRS1 (PS1) survey observed the 30,000 deg$^{2}$ of sky north of
declination $\delta = -30$ degrees in the five $grizy$ filters.  PS1
is the first part of Pan-STARRS to be completed and is the basis for
the DR1. \citet{Chambers2016}, \citet{Magnier2016a},
\citet{Waters2016}, \citet{Magnier2016b}, \citet{Magnier2016c} and
\citet{Flewelling2016} describe the instrument, survey, and data
analyses.  The principal science product of the PS1 survey is the
catalog accessible through the CasJobs interface.

We query and return the mean PSF magnitudes from the $grizy$ filters
({\tt MeanPSFMag}) which are in the AB system for our 463 VH$z$Q
sample. Our SQL and links to the main PS1 DR1 tables are given in
Appendix~\ref{sec:PS1_SQL}.

\subsection{Near-infrared photometry}~\label{sec:NIR_data} 
The near-infrared data in this paper comes from the Wide Field
Astronomy Unit's \href{https://www.roe.ac.uk/ifa/wfau/}{(WFAU)}
Science Archives for UKIRT-WFCAM, the WFCAM Science Archive
\citep[WSA; ][]{Hambly2008} and VISTA-VIRCAM, the VISTA Science
Archive \citep[VSA; ][]{Cross2012}. These archives were developed for
the VISTA Data Flow System \citep[VDFS][]{VDFS}.

We access both the WSA and the VSA and include all non-proprietary
WFCAM data, which covers all public surveys and PI projects from
Semester 05A to 2017-Jan-01, and all non-proprietary VISTA data, which
covers all public surveys and PI projects from science verification on
2009-Oct-15 to 2016-Apr-01.

Here we are not just quering the WSA or VSA data tables. We are taking
a list of objects (positions) are performing matched aperature
(``forced'') photometry on the NIR imaging data. As such, we generate
a set of tables that are different in subtle ways to the regular
``Detection'' tables.  The two most important tables for our needs are
the {\tt [w/v]serv1000MapRemeasurement} and {\tt
[w/v]serv1000MapRemeasAver}.

We produce and provide a two new databases with all the necessary
quantaties and measurements to fully reproduce our tables, figures and
results herein. Morever, these databases report considerably more
information than we report here. Full documentation can be found at
the \href{http://wsa.roe.ac.uk/www/wsa_browser.html}{WSA Schema
Browser} and the
\href{http://horus.roe.ac.uk/vsa/www/vsa_browser.html}{VSA Schema
Browser}.

  \subsubsection{Averaging matched photometry}
  The data was processed using a matched-aperture photometry method
  where flux is measured at the spectroscopic position of the quasar,
  without necessarily knowing if there is a formal detection in the NIR
  photometry beforehand. The matched-aperture pipeline is discussed in
  \citet{Cross2013} and with fuller details to appear in a forthcoming
  paper (Cross et al., 2019, in prep).

  We query the WSA and VSA performing matched-aperature photometry at
  the positions of our 463 VH$z$Qs. This database is world-readable and
  we give the full receipe and relevant SQL queries for accessing both
  databases in Appendix~\ref{sec:SQL} as well as online.

  The photometry in a single epoch image often has low
  signal-to-noise.  The advantage of matched aperture photometry on
  quasars is that co-adding is relatively simple if each epoch is taken
  in the same aperture and the aperture photometry has been corrected to
  total. Indeed, the standard aperture corrections work well for point
  sources. Coadding using the matched-aperature photometry, where the
  individual epochs are taken from multiple projects with different
  pointings and orientations, should help with issues such as scattered
  light, pixel distortion and aperture corrections.

@@

  We calculate a set of averaged catalogues, for each pointing and filter, based
  on the requirements in \verb+RequiredMapAverages+, in these cases over time
  spans of 7, 14, 30, 91, 183 days, 365 days, 730 days, over 10 epochs and
  over all epochs. The averaging process starts at the first epoch and works onwards 
  from there. Again, we present these measurements in the new SQL tables.

@@

\subsection{MIR data}
The MIR data for this study comes from the Wide-field Infrared Survey
Explorer (WISE) mission, and we utlize data from the WISE cryogenic
and NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey
phases.

We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fourth-year of NEOWISE-R operations \citep[2017 December;]{Mainzer2011}.  More specifically, we utilise the recently released ``unWISE Catalog'' \citet{MeisnerSchlafly2019}. The unWISE effort\footnote{http://unwise.me/} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}. %{\bf Few more words here on the unWISE catalog...}.

@@

@@
